Convolutional equivalent layer for gravity data processing

### 2019-11-29 manuscript/manuscript.tex
review the application to synthetic data
change the title

\title{Fast equivalent-layer technique for gravity data processing with BTTB matrix systems}

@@

%\address{
%\footnotemark[1]Observat\'{o}rio Nacional, \\
%Department of Geophysics, \\
%Rio de Janeiro, Brazil}
%\author{Diego Takahashi\footnotemark[1], Vanderlei C. Oliveira{ }Jr.\footnotemark[1] and 
%Val{\'e}ria C. F. Barbosa\footnotemark[1]}
%
%\footer{vanderlei@on.br}
%\lefthead{Takahashi, Oliveira{ }Jr. \& Barbosa}
%\righthead{Fast equivalent-layer for BTTB systems}

@@

% Main body
\include{abstract}
\include{introduction}
\include{methodology}
\include{synthetic_data}
\include{field_data}
\include{conclusions}
\include{aknowledgements}

>>>>

\title{Convolutional equivalent layer for gravity data processing}

@@

\address{
\footnotemark[2]Observat\'{o}rio Nacional, Department of Geophysics, Rio de Janeiro, Brazil\\
\footnotemark[1] Corresponding author: diego.takahashi@gmail.com
}
\author{Diego Takahashi\footnotemark[2]\footnotemark[1], Vanderlei C. Oliveira{ }Jr.\footnotemark[2] and 
Val{\'e}ria C. F. Barbosa\footnotemark[2]}

%\footer{Example}
%\lefthead{Takahashi, Oliveira{ }Jr. \& Barbosa}
\righthead{Convolutional equivalent layer}

@@

% Main body
\include{abstract}
\include{introduction}
\include{methodology}
\include{synthetic_data}
\include{field_data}
\include{conclusions}
%\include{aknowledgements}
